%======================================================================
\chapter{Introduction}
%======================================================================

Proteins perform a wide variety of biochemical functions in organisms including facilitating cell signaling, acting as enzymes, and comprising structural components. While the information necessary for continuation of life is encoded by DNA, the dynamic process of regulation, maintenance, and reproduction are carried out by proteins.

The differentiating factor for proteins is their sequence of amino acids, dictated by the nucleotide sequence of their genes. This sequence encodes the specific amino acid residues and their position in the polypeptide chain which are the determining factors for how a protein will fold and form its three-dimensional structure. 
In some of his most influential work, Nobel laureate Christian B. Anfinsen \cite{anfinsen.article} concluded that the stable 3-D structure of a protein is determined by its linear amino acid sequence. However, this relationship does not imply similar amino acid sequences always fold similarly, it is often the case that sequences differing by only a few residues exhibit entirely different conformations. Structures can also differ based on environmental factors as well; similar proteins fold differently based on where they are found.

Determining the three-dimensional atomic structure of a protein's amino acid sequence is critical for understanding it's function; a misfolded folded protein may exhibit modified or no behaviour. This is postulated to be the cause of several neurodegenerative diseases (see prion diseases LINK). Accordingly, predicting structure from the corresponding amino acid sequence constitutes an important challenge known as the \textit{Protein Folding Problem}. 

Traditionally, protein structure has been individually determined through identifying its coding sequence and then utilizing laboratory techniques such as X-ray crystallography and nuclear magnetic resonance (NMR) spectroscopy. However, these techniques are slow and costly while advancements in genome sequencing have lead to exponential growth of the protein sequence data. The experimentally validated structural data only comprises a minute proportion of known protein sequences. Furthermore, there is growing interest in designing amino acid sequences to achieve a specified function such as creating effective drugs (CITE). Thus development of computational methods for structure prediction is highly desirable. 

%----------------------------------------------------------------------
\section{Energy Scoring}
%----------------------------------------------------------------------

An essential physical phenomenon 

\section{Some Meaningless Stuff}

The credo of the \gls{aaaaz} was, for several years, several paragraphs of gibberish, until the \gls{dingledorf} responsible for the \gls{aaaaz} Web site realized his mistake:

"Velit dolor illum facilisis zzril ipsum, augue odio, accumsan ea augue molestie lobortis zzril laoreet ex ad, adipiscing nulla. Veniam dolore, vel te in dolor te, feugait dolore ex vel erat duis nostrud diam commodo ad eu in consequat esse in ut wisi. Consectetuer dolore feugiat wisi eum dignissim tincidunt vel, nostrud, at vulputate eum euismod, diam minim eros consequat lorem aliquam et ad. Feugait illum sit suscipit ut, tation in dolore euismod et iusto nulla amet wisi odio quis nisl feugiat adipiscing luptatum minim nisl, quis, erat, dolore. Elit quis sit dolor veniam blandit ullamcorper ex, vero nonummy, duis exerci delenit ullamcorper at feugiat ullamcorper, ullamcorper elit vulputate iusto esse luptatum duis autem. Nulla nulla qui, te praesent et at nisl ut in consequat blandit vel augue ut.

Illum suscipit delenit commodo augue exerci magna veniam hendrerit dignissim duis ut feugait amet dolor dolor suscipit iriure veniam. Vel quis enim vulputate nulla facilisis volutpat vel in, suscipit facilisis dolore ut veniam, duis facilisi wisi nulla aliquip vero praesent nibh molestie consectetuer nulla. Wisi nibh exerci hendrerit consequat, nostrud lobortis ut praesent dignissim tincidunt enim eum accumsan. Lorem, nonummy duis iriure autem feugait praesent, duis, accumsan tation enim facilisi qui te dolore magna velit, iusto esse eu, zzril. Feugiat enim zzril, te vel illum, lobortis ut tation, elit luptatum ipsum, aliquam dolor sed. Ex consectetuer aliquip in, tation delenit dignissim accumsan consequat, vero, et ad eu velit ut duis ea ea odio.

Vero qui, te praesent et at nisl ut in consequat blandit vel augue ut dolor illum facilisis zzril ipsum. Exerci odio, accumsan ea augue molestie lobortis zzril laoreet ex ad, adipiscing nulla, et dolore, vel te in dolor te, feugait dolore ex vel erat duis. Ut diam commodo ad eu in consequat esse in ut wisi aliquip dolore feugiat wisi eum dignissim tincidunt vel, nostrud. Ut vulputate eum euismod, diam minim eros consequat lorem aliquam et ad luptatum illum sit suscipit ut, tation in dolore euismod et iusto nulla. Iusto wisi odio quis nisl feugiat adipiscing luptatum minim. Illum, quis, erat, dolore qui quis sit dolor veniam blandit ullamcorper ex, vero nonummy, duis exerci delenit ullamcorper at feugiat. Et, ullamcorper elit vulputate iusto esse luptatum duis autem esse nulla qui.

Praesent dolore et, delenit, laoreet dolore sed eros hendrerit consequat lobortis. Dolor nulla suscipit delenit commodo augue exerci magna veniam hendrerit dignissim duis ut feugait amet. Ad dolor suscipit iriure veniam blandit quis enim vulputate nulla facilisis volutpat vel in. Erat facilisis dolore ut veniam, duis facilisi wisi nulla aliquip vero praesent nibh molestie consectetuer nulla, iriure nibh exerci hendrerit. Vel, nostrud lobortis ut praesent dignissim tincidunt enim eum accumsan ea, nonummy duis. Ad autem feugait praesent, duis, accumsan tation enim facilisi qui te dolore magna velit, iusto esse eu, zzril vel enim zzril, te. Nisl illum, lobortis ut tation, elit luptatum ipsum, aliquam dolor sed minim consectetuer aliquip.

Tation exerci delenit ullamcorper at feugiat ullamcorper, ullamcorper elit vulputate iusto esse luptatum duis autem esse nulla qui. Volutpat praesent et at nisl ut in consequat blandit vel augue ut dolor illum facilisis zzril ipsum, augue odio, accumsan ea augue molestie lobortis zzril laoreet. Ex duis, te velit illum odio, nisl qui consequat aliquip qui blandit hendrerit. Ea dolor nonummy ullamcorper nulla lorem tation laoreet in ea, ullamcorper vel consequat zzril delenit quis dignissim, vulputate tincidunt ut."